StackTokens: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-02 fully-abstract-comp/popl2019/preamble-illu.tex
Update layout of capability braces - add command for linear cap brace.

\newcommand{\capbrace}[4][sp1]{
  \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
  #2 -- #3 node (#1) [black,midway,xshift=1cm,align=center] {\footnotesize #4};
}

\newcommand{\capbracebot}[4][sp1]{
  \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt,aspect=0.25},yshift=0pt]
  #2 -- #3 node (#1) [black,near start,xshift=1cm,align=center] {\footnotesize #4};
}

\newcommand{\capbracebotred}[4][sp1]{
  \draw [decorate,red,decoration={brace,amplitude=10pt,mirror,raise=4pt,aspect=0.25},yshift=0pt]
  #2 -- #3 node (#1) [red,near start,xshift=1cm,align=center] {\footnotesize #4};
}

>>>>

\newcommand{\capbrace}[4][sp1]{
  \draw [decorate,decoration={brace,amplitude=7pt,mirror,raise=4pt},yshift=0pt]
  #2 -- #3 node (#1) [black,midway,xshift=1cm,align=center] {\footnotesize #4};
}

\newcommand{\lincapbrace}[4][sp1]{
  \draw [densely dotted,decorate,decoration={brace,amplitude=7pt,mirror,raise=4pt},yshift=0pt]
  #2 -- #3 node (#1) [black,midway,xshift=1cm,align=center] {\footnotesize #4};
}

\newcommand{\capbracebot}[4][sp1]{
  \draw [decorate,decoration={brace,amplitude=7pt,mirror,raise=4pt,aspect=0.25},yshift=0pt]
  #2 -- #3 node (#1) [black,near start,xshift=1cm,align=center] {\footnotesize #4};
}

\newcommand{\capbracebotred}[4][sp1]{
  \draw [decorate,red,decoration={brace,amplitude=7pt,mirror,raise=4pt,aspect=0.25},yshift=0pt]
  #2 -- #3 node (#1) [red,near start,xshift=1cm,align=center] {\footnotesize #4};
}
